%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {UniFi-OS Storage Software Engineer} % Job title
    {Ubiquiti Inc.} % Organization
    {Taiwan/Remote} % Location
    {Mar. 2022 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {
          Pioneered the software and firmware development of Ubiquiti’s first
          NAS under constrained resources, involving in hardware bringup,
          strategic planning, user-centric solution design and iterative
          refinement, contributing to market success and product line expansion.
          }
          \begin{itemize}
          \item {
            Ported the BSP and uboot FIT image to AL324 board,
            preparing factory production tests.
            }
          \item {
            Collaborating on designing, developing and testing core NAS features
            on Debian OS, including storage management, filesystem (FS)
            services, network discovery and system-data migration.
            }
          \item {
            Upgraded Linux from 4.19 to 5.10, resolving Alpine SDK, PCI, RAID,
            AHCI and PHY regressions. Holistically verified
            system stability and performance with Phoronix Test Suites,
            packetdrill, xfstest. Brought in a 40\% improvement in
            write IOPS with optimized Btrfs disk I/O scheduling.
            }
          \item {
            Boosted transfer rates by 38\% (upload) and 55\% (download),
            reaching 830/940 MB/s over 10GbE.
            }
          \item {
            Reduced cross-device copies, quota accounting and data leakage
            with the FS layout redesign.
            }
          \item {
            Minimized the latency of Btrfs subvolume deletions, making it
            orthogonal to the number of files.
            }
          \end{itemize}
        \item {
          Brought system stability and performance improvements to all
          UniFi-OS products.
          }
          \begin{itemize}
          \item {
            Optimized an exporter CLI in Python, reducing CPU usage by 65\% and
            memory usage by 50\%, leading to a 30\% decrease in system load.
            Introduced a gRPC state exporter for lightweight streaming
            notifications, eliminating most latency from seconds to
            microseconds.
            }
          \item {
            Fixed an OOM bug due to socket misallocations, improving 64kB
            page-sized system reliability.
            }
          \end{itemize}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {QNAP Systems Inc.} % Organization
    {Taiwan} % Location
    {Jan. 2018 - Feb. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {
          Took full part in Hybridmount, a FS as cloud storage gateway,
          deployed on 190K QNAP devices as of 2021, capable of video streaming,
          content caching and access via file-sharing protocols.
          }
        \begin{itemize}
          \item {
            Designed and implemented the database schema, CLI, IPC and loopback-FS
            cache management.
            }
          \item {
            Ensured software quality by composing unit, integration and
            stress tests, incorporating public suites (pjdfstest and filebench)
            and building automated CI pipelines using Jenkins and Docker.
            Handled fewer than 20 support tickets since the first official
            release.
            }
          \item {
            Reduced duration of compiling codes from 30 minutes to fewer
            than 10 minutes.
            }
          \item {
            Reduced the time to create 50 million files from 60 days
            on SSDs to less than 7 days on HDDs.
            }
          \item {
            Continuously improved runtime performance, achieving a 50\%
            increase in sequential write speed, 10\% random read, 300\% metadata
            operations through various optimizations, including filename
            hashing, file read-ahead, multi-threading, fine-grained locking, VFS
            caching and database index.
            }
          \item {
            Successfully utilized VFS dcache by carefully handling unicode
            normalization and case sensitivity.
            }
        \end{itemize}
      \item {
        Implemented key features in deduplication FS, including write-back cache
        and chunk defragmentation.
        }
        \begin{itemize}
          \item {
            Refactored read/write operations, consequently reducing the related
            codebase by 50\% and fixing abnormal data assembly at chunk edges.
            }
        \end{itemize}
      \item {
        Developed a POC of a POSIX-compliant cloud-tiering FS with FUSE, IPFS in
        Go.
        }
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
